Tuning parameter selection for a penalized estimator of species richness

### 2019-07-10 rre_manuscript/paper.tex
data analysis results table added

\newrgbcolor{alexcolor}{.1 .7 .7}
\ifthenelse {\boolean{DEBUG}}
{\newcommand{\alex}[1]{{\bf \alexcolor{[\@alex: #1]}}}}
{\newcommand{\alex}[1]{}}

@@

\amy{Happy to discuss, but I think it's probably easiest for me to be corresponding author, because you won't have your UW e-mail forever}

@@

>>>>

\newrgbcolor{alexcolor}{.1 .7 .7}
\ifthenelse {\boolean{DEBUG}}
{\newcommand{\alex}[1]{{\bf \alexcolor{[\@Alex: #1]}}}}
{\newcommand{\alex}[1]{}}

@@

\amy{Happy to discuss, but I think it's probably easiest for me to be corresponding author, because you won't have your UW e-mail forever}
\alex{Having you as the corresponding author sounds great, just didn't want to volunteer you for unwanted emails until we discussed!}

@@

\section{Data Analysis}
\label{sec:data_analysis}

\alex{Data analysis writeup is forthcoming.  For now, here are the results with the same C grid we used in simulations.   I will give more thought into the best way to display these.}

\begin{table}[h]
\tblcaption{Estimates using a series of three samples drawn in consecutive years from the lakes data.  Only replicates from the Summer months and the Littoral region of the lake are included in the samples.  $\widehat{C}_{[\text{method}]}$ is the $C$ estimate obtained using the methods defined in Section \ref{sec:tuning_proposals}, shown for each sample.  The number of replicates in each sample is given by $r$.
\label{tab:data_analysis}}
\centering
\begin{tabular}{|r|r|r|r|}
  \hline
& 2009  & 2010 & 2011 \\ 
  \hline
$\widehat{C}_{[0]}$ & 11200 & 11440 & 14014 \\ 
  $\widehat{C}_{[1]}$ & 9645 & 11139 & 12246 \\ 
  $\widehat{C}_{[2]}$ & 10612 & 11120 & 11946 \\ 
  $\widehat{C}_{[3]}$ & 11200 & 11440 & 14014 \\ 
  $\widehat{C}_{[4]}$ & 10744 & 11165 & 10328 \\ 
   \hline
     $r$ & 8 & 6 & 6 \\
  \hline
\end{tabular}
\end{table}

\noindent \alex{The reason for running an expanded C grid is that many of the estimates in this table are near the boundary of our grid (11,200, 11,440 and 14,300 respectively).  I'm not concerned that the estimates might be too large/bad, but I am concerned that this may be obscuring differences between the methods.}
